\LARGE \bf Steering a Swarm Using Global Inputs\\ and Swarm Statistics

### 2017-10-03 journalSwarmControl/Reviews/Response.tex

	\Reviewer{\#3}\response{In the paper the terms: micro, nano robots, and particles are used interchangeably, that is perfectly fine, however, it would be better in the very beginning to make that clear possible with a footnote, especially the use of the term particles. }

	Good point. We have edited the paper so that references to micro and nano robots are only in the introduction, related work, and conclusion. We have replaced 
	``robot'' with ``particle'' unless the object to be controlled is a hardware robot (such as a kilobot).
	Additionally, in paragraph 1 we now state ``Instead, this paper treats the robots as particles that are steered by a global control signal broadcast to the entire population."

	\response{In page two, column 1 , the authors state that "process noise cancels the differentiating effects... tens of robots." The term tens of robots is not clear. It would also help a citation if it exists.}
	This has been clarified by modifying text and adding references:
	``Similarly, our previous work, [16], [17], focused on exploiting inhomogeneity between robots. These control algorithms theoretically apply to any number of robots, even robotic continuums. However, all these works never controlled more than twelve robots at a time because process noise cancels the differentiating effects of robot inhomogeneity. We desire control algorithms that extend to many thousands of robots.''

	\response{Throughout the paper citations [?] are used as nouns, while that is quite common practice the paper reads better when the authors are used. e.g. "[123] shows that..." instead use: "Joe and Bob [123] show that..."  }
	That is a good idea, but made the paper over the page limit.  Instead we have worked to minimize the number of times references are used as nouns.

### 2017-10-03 journalSwarmControl/conclusion.tex
Handing over to Shiva

Inspired by the three lessons from swarmcontrol.net, this paper designed controllers and controllability results using only the mean and variance of a particle swarm. 
We developed a hysteresis based controller to regulate the position and variance of a swarm. We designed a controller for object manipulation using policy iteration for path planning, regions for outlier rejection, and potential fields for minimizing moving the object backwards. 
All automatic controllers were implemented using 100 kilobots steered by the direction of a global light source.
These experiments culminated in an object manipulation task in a workspace with obstacles.

>>>>

Inspired by the three lessons from \href{www.swarmcontrol.net}{SwarmControl.net}, this paper designed controllers and controllability results using only the mean and variance of a particle swarm. 
We developed a hysteresis based controller to regulate the position and variance of a swarm. We designed a controller for object manipulation using policy iteration for path planning, regions for outlier rejection, and potential fields for minimizing moving the object backwards. 
All automatic controllers were implemented using 100 kilobots steered by the direction of a global light source.
These experiments culminated in an object manipulation task in a workspace with obstacles.

### 2017-10-03 journalSwarmControl/expResults.tex
Handing over to Shiva

We designed six experiments to investigate human control of large swarms for manipulation tasks.  Screenshots of representative experiment are shown in Fig.~\ref{fig:5experiments}.  Each experiment examined the effects of varying a single parameter: population of particles for manipulation, four levels of visual feedback, different levels of Brownian noise.%, position control with 1 to 10 particles, and three control architectures for both assembly and foraging tasks. 
 The users could choose which experiment to try, and our architecture randomly assigned a parameter value for each trial.  We recorded the completion time and the participant ID for each successful trial.  
%As Fig.~\ref{fig:Learning} shows, one-third of all participants played only a single game.  Still, many played multiple games, and their decreasing completion times demonstrates their skills improved.

>>>>

We designed six experiments to investigate human control of large swarms for manipulation tasks.  Screenshots of representative experiments are shown in Fig.~\ref{fig:5experiments}.  Each experiment examined the effects of varying a single parameter: population of particles for manipulation, four levels of visual feedback, different levels of Brownian noise.  %, position control with 1 to 10 particles, and three control architectures for both assembly and foraging tasks. 
 The users could choose which experiment to try, and our architecture randomly assigned a parameter value for each trial.  We recorded the completion time and the participant ID for each successful trial.  
%As Fig.~\ref{fig:Learning} shows, one-third of all participants played only a single game.  Still, many played multiple games, and their decreasing completion times demonstrates their skills improved.

### 2017-10-03 journalSwarmControl/relatedWork.tex
Shiva and Aaron worked on the reviewers' comments.
Only thing left is E and snail mazes
Handing over to Shiva

This paper investigates global control of particles that have no onboard computation. This prevents us from applying controllers that require computation on the agents, as in \cite{milutinovic2006modeling,prorok2011multi,demir2015probabilistic}.
%\cite{milutinovic2006modeling} requires robots that can execute task primitives.  Our particles simply move in the direction of the global control unless they are stopped by an obstacle. 
%\cite{palmer2011hamiltonian} uses only Open-Loop control.  Our submission relies on state feedback 
%\cite{prorok2011multi} requires collective intelligence of a group of miniature robots
%\cite{demir2015probabilistic} requires robots that can individually decide when to actuate and when to remain anchored, can perform onboard computation (generate a random number, calculate its bin and the next bin). 
Another control paradigm is to construct robots with physical heterogeneity so that they respond differently to a global broadcast control signal.  Examples include \emph{scratch-drive microrobots}, actuated and controlled by a DC voltage signal from a substrate by \cite{Donald2006,Donald2008};  magnetic structures  with different cross-sections that can be independently steered by \cite{Floyd2011,Diller2013};  \emph{MagMite} microrobots with different resonant frequencies and a global magnetic field by \cite{Frutiger2008}; and  magnetically controlled nanoscale helical screws constructed to stop movement at different cutoff frequencies of a global magnetic field by
\cite{Tottori2012} and \cite{Peyer2013}. 
Similarly, our previous work, \cite{Becker2012,Becker2012k}, focused on exploiting inhomogeneity between robots.  These control algorithms theoretically apply to any number of robots, even robotic continuums.

However, process noise cancels the differentiating effects of inhomogeneity for more than tens of robots.  We desire control algorithms that extend to many thousands of robots.
Limited position control was achieved by \cite{bretl2007control} and our previous work \cite{beckerIJRR2014}, but both used robots commanded in their local coordinate frame. Our new submission focuses on a more common paradigm: particles commanded in a global coordinate frame

@@

Human \emph{fanout}, the number of robots a single human user could directly control is studied in \cite{Jr2004}.  %Studied as a key aspect of human-robot interaction, 
They postulated that the optimal number of robots was approximately  the autonomous time  divided by the interaction time required by each robot.  Their sample problem involved a multi-robot search task, where users could assign goals to robots.  Their user interaction studies with simulated planar robots  indicated a \emph{fanout plateau} of about 8 robots, with diminishing returns for more robots.   They hypothesized the location of this plateau is highly dependent on the underlying task.  Indeed, our paper indicates there are tasks without plateaus. % (Lemmings is an example of this as well, for systems with autonomy
Their research investigated robots with 3 levels of autonomy.  We use robots without autonomy, corresponding with their first-level robots.

@@

Our $n$-robot system with 2 control inputs and 4$n$ states is inherently under-actuated, and superficially bears resemblance to compliant, under-actuated manipulators.  Our swarms conform to the object to be manipulated, but lack the restoring force provided by flexures in \cite{odhner2014compliant} or silicone in \cite{deimel2014novel}.  Our swarms tend to disperse and so to regroup them we require artificial forces like the variance control primitives in \S \ref{sec:VarianceControl}.

>>>>

This paper investigates global control of particles that have no onboard computation. This prevents us from applying controllers that require computation on the agents, as in \cite{milutinovic2006modeling,prorok2011multi,demir2015probabilistic}.
%\cite{milutinovic2006modeling} requires robots that can execute task primitives.  Our particles simply move in the direction of the global control unless they are stopped by an obstacle. 
%\cite{palmer2011hamiltonian} uses only Open-Loop control.  Our submission relies on state feedback 
%\cite{prorok2011multi} requires collective intelligence of a group of miniature robots
%\cite{demir2015probabilistic} requires robots that can individually decide when to actuate and when to remain anchored, can perform onboard computation (generate a random number, calculate its bin and the next bin). 
Another control paradigm is to construct robots with physical heterogeneity so that they respond differently to a global broadcast control signal.  Examples include \emph{scratch-drive microrobots}, actuated and controlled by a DC voltage signal from a substrate by \cite{Donald2006,Donald2008};  magnetic structures  with different cross-sections that can be independently steered by \cite{Floyd2011,Diller2013};  \emph{MagMite} microrobots with different resonant frequencies and a global magnetic field by \cite{Frutiger2008}; and  magnetically controlled nanoscale helical screws constructed to stop movement at different cutoff frequencies of a global magnetic field by
\cite{Tottori2012} and \cite{Peyer2013}. 
Similarly, our previous work, \cite{Becker2012,Becker2012k}, focused on exploiting inhomogeneity between robots.  These control algorithms theoretically apply to any number of robots, even robotic continuums.
However, all these works never controlled more than twelve robots at a time because process noise cancels the differentiating effects of robot inhomogeneity.
%However, a consequence of the central limit theorem is that independent process noise cancels the differentiating effects of inhomogeneity for large numbers of robots. 
 We desire control algorithms that extend to many thousands of robots.
Limited position control was achieved by \cite{bretl2007control} and our previous work \cite{beckerIJRR2014}, but both used robots commanded in their local coordinate frame. Our new submission focuses on a more common paradigm: particles commanded in a global coordinate frame.

@@

Human \emph{fanout}, the number of robots a single human user could directly control is studied in \cite{Jr2004}.  %Studied as a key aspect of human-robot interaction, 
They postulated that the optimal number of robots was approximately  the autonomous time  divided by the interaction time required by each robot.  Their sample problem involved a multi-robot search task, where users could assign goals to robots.  Their user interaction studies with simulated planar robots  indicated a \emph{fanout plateau} of about 8 robots, with diminishing returns for more robots.   They hypothesized the location of this plateau is highly dependent on the underlying task.  Indeed, our paper indicates there are tasks without plateaus. % (Lemmings is an example of this as well, for systems with autonomy
Their research investigated robots with three levels of autonomy.  We use robots without autonomy, corresponding with their first-level robots.

@@

Our $n$-robot system with 2 control inputs and 4$n$ states is inherently under-actuated, and superficially bears resemblance to compliant, under-actuated manipulators.  Our swarms conform to the object to be manipulated, but lack the restoring force provided by flexures in~\cite{odhner2014compliant} or silicone in~\cite{deimel2014novel}.  Our swarms tend to disperse and so to regroup them we require artificial forces like the variance control primitives in \S \ref{sec:VarianceControl}.
